Generalised Management Strategy Evaluation: modelling biodiversity and food security

### 2019-01-04 notebook/presentation/GMSE_presentation.Rmd
Add near to end

```{r, echo = FALSE}
mod <- gmse_apply(res_mod = function(N_0 = 200, K = 2000, gr = 0.3) N_1 <- N_0 + gr * N_0 * ( 1 - N_0/K ), stakeholders = 5);
```

```{r, eval = FALSE}
mod <- gmse_apply(res_mod = logistic_res_mod, # Custom model
                  N_0 = 200, gr = 0.3,        # Custom arguments
                  stakeholders = 5);          # GMSE arguments
```

@@

>>>>

```{r, echo = FALSE}
mod <- gmse_apply(res_mod = function(N_0 = 200, K = 2000, gr = 0.3) N_1 <- N_0 + gr * N_0 * ( 1 - N_0/K ), stakeholders = 2);
```

```{r, eval = FALSE}
mod <- gmse_apply(res_mod = logistic_res_mod, # Custom model
                  N_0 = 200, gr = 0.3,        # Custom arguments
                  stakeholders = 2);          # GMSE arguments
```

@@

## Social conflict & management

**General idea**

- Detail 1
- Detail 2
- Detail 3

![](cusack.png)

![](gmse_power.png)

## Social conflict & management

Results

## Future work PhD

![](bach.jpeg)

**General idea of the paper**

- Detail 1
- Detail 2
- Detail 3

## Future work ML

Saro pictures

## Future work ML

Where next version will go

## Summary and links
